\fakebf{HIV virulence evolution in structured epidemic models}

### 2016-06-01 poster/hivlhs_eeid2016.Rnw
fix size (R)

%% You can change the poster orientation (portrait vs. landscape) and the paper size (a0, a1, &c.) here:
\usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength{\columnheight}
\setlength{\columnheight}{105cm}

\newlength{\topcolumnheight}
\setlength{\topcolumnheight}{50cm}

@@

\vspace{-2.4 cm} % shouldn't need this??
\begin{block}{Summary}
\noindent
\hspace{-1.6cm}
Pathogens can evolve rapidly in response to changing
conditions (e.g., epidemic stage or public health interventions). 
Models of \textbf{eco-evolutionary dynamics} often
neglect important epidemiological processes, such as the 
dynamics of sexual partnerships. We
compared \textbf{models with a range of complexity} 
of partnership dynamics and extra-partnership contact.
\end{block}

@@

\begin{column}{.65\textwidth}

\begin{columns}
  \begin{column}{.5\textwidth}
    \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
      \begin{minipage}[T]{.95\textwidth}
        \parbox[t][\topcolumnheight]{\textwidth}{

@@

\begin{itemize}
\item \textbf{80\% of total variability} in peak SPVL is among- vs. within-model
\item least (random) and most (pairform+epc) models \textbf{most similar}:
  single individuals and extra-pair contact wash out effects of structure
\item implicit model is \textbf{most different}
\item random-mixing model underestimates variability
\end{itemize}

@@

            \begin{block}{Univariate summaries}
              \includegraphics[width=0.7\textwidth]{figure/univ_scheme.pdf}

              \vspace{1cm}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
\begin{itemize}
\item peak timing: epc $>$ finite pair-formation effects
\item equilibrium virulence: interaction
\item low-equilibrium outcomes for intermediate-complexity models
\end{itemize}

@@

\begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
  \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
    \parbox[t][30cm]{\textwidth}{ % must be some better way to set

>>>>

%% You can change the poster orientation (portrait vs. landscape) and the paper size (a0, a1, &c.) here:

\usepackage[orientation=portrait,size=custom,width=71,height=102,scale=1.2,debug]{beamerposter}
%## size=a0,

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength{\columnheight}
\setlength{\columnheight}{100cm}

\newlength{\topcolumnheight}
\setlength{\topcolumnheight}{37cm}

@@

\vspace{-1 cm} % shouldn't need this??
\begin{block}{Summary}
\noindent
\hspace{-1.6cm}
Pathogens can evolve rapidly in response to changing
conditions (e.g., epidemic stage or public health interventions). 
Models of \textbf{eco-evolutionary dynamics} often
neglect important epidemiological processes, such as the 
dynamics of sexual partnerships. We
compared \textbf{models with a range of complexity} 
of partnership dynamics and extra-partnership contact.
\end{block}

@@

%\newcommand{\topfudge}{-5cm}

\begin{column}{.65\textwidth}
\begin{columns}
  \begin{column}{.5\textwidth}
    \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
      \begin{minipage}[T]{.95\textwidth}
        \parbox[t][\topcolumnheight]{\textwidth}{ 
          \vspace{-4.5cm} % shouldn't need this??

@@

\begin{itemize}
\item \textbf{80\% of total variability} in peak SPVL is among- vs. within-model
\item least (random) and most (pairform+epc) models \textbf{most similar}:
  single individuals and extra-pair contact wash out effects of structure
%\item implicit model is \textbf{most different}
\item random-mixing model underestimates variability
\end{itemize}

@@

\vspace{-4.5cm} % shouldn't need this??
            \begin{block}{Univariate summaries}
              \includegraphics[width=0.7\textwidth]{figure/univ_scheme.pdf}

              \vspace{1cm}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
\begin{itemize}
\item peak timing: epc $>$ finite pair-formation effects
\item equilibrium virulence: interaction
%\item low-equilibrium outcomes for intermediate-complexity models
\end{itemize}

@@

\begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
  \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
    \parbox[t][26cm]{\textwidth}{ % must be some better way to set
